---
title: "Critical values adjusted for bandwidth snooping"
author: "Michal Kolesár"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: false
    number_sections: true
    includes:
      in_header: header.tex
bibliography: library.bib
vignette: >
  %\VignetteIndexEntry{Critical values adjusted for bandwidth snooping}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, cache=FALSE}
library("knitr")
knitr::opts_knit$set(self.contained = FALSE)
knitr::opts_chunk$set(tidy = TRUE, collapse=TRUE, comment = "#>",
                      tidy.opts=list(blank=FALSE, width.cutoff=75))
```


# Calculation of critical values

This section describes the method used to tabulate the critical values based on
Corollary 3.1 in @ArKo15snooping.

Let $k$ be a kernel (i.e.\ a non-negative function symmetric around zero that
integrates to one) with bounded support normalized to $[-1,1]$. We want to
compute the quantiles of
\begin{equation}\label{eq:1}
  \sup_{1\leq h\leq t}
  \mathbb{H}(h)=_{d}\sup_{1/t\leq h\leq 1}\mathbb{H}(h),\qquad\text{and}\quad
  \sup_{1\leq h\leq t}
  |\mathbb{H}(h)|=_{d}\sup_{1/t\leq h\leq 1}|\mathbb{H}(h)|
\end{equation}
where $=_{d}$ means "equals in distribution", and $\mathbb{H}(h)$ is a mean-zero
Gaussian process with covariance function
$$ \cov(\mathbb{H}(h),\mathbb{H}(h'))=\frac{\int_{-\infty}^{\infty}
    k(u/h)k(u/h') \, \dd u}{ \sqrt{\int_{-\infty}^{\infty} k(u/h)^{2}\, \dd
    u\cdot \int_{-\infty}^{\infty} k(u/h')^{2}\, \dd u} }
    =\frac{\int_{0}^{\infty} k(u/h)k(u/h') \, \dd u}{ \sqrt{hh'}
    \int_{0}^{\infty} k(u)^{2}\, \dd u}. $$

Let $\{Y_{i,m}\}_{1\leq i\leq T,1\leq m\leq S}$ be independent samples from a
standard normal distribution, where $T$ is the number of points sampled in each
simulation draw $m$, and $S$ is the number of simulation draws. Let
\begin{equation*}
  \hat{\mathbb{H}}_{m}(h)=\frac{1/\sqrt{T}
    \sum_{i=1}^{T}Y_{i,m}k\left(i/hT\right)}{\sqrt{T^{-1}
    \sum_{i=1}^{T} k(i/hT)^2}}.
\end{equation*}
Observe that $(\hat{\mathbb{H}}_{m}(h))_{h\in (0,1]}$ is a centered
Gaussian process with covariance function
\begin{equation*}
    \E[\hat{\mathbb{H}}_{m}(h)\hat{\mathbb{H}}_{m}(h')]=
    \frac{1/T\sum_{i=1}^{T}k(i/hT)k(i/h'T)}{ \sqrt{T^{-1} \sum_{i=1}^{T}
    k(i/hT)^2}\sqrt{T^{-1} \sum_{i=1}^{T} k(i/h'T)^2}}.
\end{equation*}
As $T\to\infty$, this process converges to $\left(\mathbb{H}(h)\right)_{h\in
  (0,1]}$, since $\E[\hat{\mathbb{H}}_{m}(h)\hat{\mathbb{H}}_{m}(h')]\to
  \cov(\mathbb{H}(h),\mathbb{H}(h'))$.

We then approximate the quantiles of the two distributions in Equation
\eqref{eq:1} by empirical quantiles based on the sample
$\{\hat{\mathbb{H}}_{m}(h)\}_{m=1}^{S}$. The process $\hat{\mathbb{H}}_{m}(h)$
is evaluated on the log-grid
\begin{equation*}
  \exp(\log(t):\text{stepsize}:\log(1)).
\end{equation*}


## Example: uniform kernel
If the kernel is uniform, then $\hat{\mathbb{H}}_{n}(h)$ simplifies to
\begin{equation*}
  \hat{\mathbb{H}}_{m}(h)=\frac{\sum_{i=1}^{\lfloor hT\rfloor}Y_{i,m}}{\sqrt{
    \lfloor hT\rfloor}}.
\end{equation*}
so that $\hat{\mathbb{H}}_{m}(h)$ is mean-zero Gaussian process with covariance
function $\E[ \hat{\mathbb{H}}_{m}(h) \hat{\mathbb{H}}_{m}(h')]=\frac{\lfloor
  hT\rfloor\wedge \lfloor h'T\rfloor}{\sqrt{\lfloor hT\rfloor \lfloor h'T\rfloor}}$.


## Note: Alternative approaches

An alternative used in an earlier version of the paper is to replace
$\hat{\mathbb{H}}_{m}(h)$ with
\begin{equation*}
  \tilde{\mathbb{H}}_{m}(h)=\frac{1/\sqrt{T}
    \sum_{i=1}^{T}Y_{i,m}k\left(i/hT\right)}{\sqrt{
      h\int_{0}^{\infty} k(u)^{2}\, \dd u}}
\end{equation*}
This method, however, has the disadvantage what for any finite $T$, the variance
of the process $\tilde{\mathbb{H}}_{m}(h)$ is not equal to one exactly.

A third possible approach is to replace $\hat{\mathbb{H}}_{m}(h)$ with
\begin{align*}
  \hat{\mathbb{H}}_j(h) =\frac{\frac{1}{\sqrt{T}}
    \sum_{i=1}^{T}Y_{i,j}k(X_i/h)}{\sqrt{\frac{1}{2A}\int k(u/h)^2\, du}}
  =\frac{\frac{1}{\sqrt{T}} \sum_{i=1}^{T}Y_{i,j}k(X_i/h)}{\sqrt{\frac{h}{2A}\int
      k(u)^2\, du}},
\end{align*}
where $\{(X_{i,j},Y_{i,j})\}_{1\le i\le T,1\le j\le S}$ be i.i.d. with $X_i$
independent of $Y_i$ and $X_i\sim U[-A,A]$ and $Y_i\sim N(0,1)$.
Note that $\hat{\mathbb{H}}_j(h)=0$ and
\begin{align*}
  \cov(\hat{\mathbb{H}}_j(h),\hat{\mathbb{H}}_j(h'))
  &=\frac{EY_{i,j}^2k(X_i/h)k(X_i/h') }{\sqrt{\frac{1}{2A}\int k(u/h)^2\,
      du}\sqrt{\frac{1}{2A}\int k(u/h')^2\, du}}
  \\
  & =\frac{Ek(X_i/h)k(X_i/h')}{\frac{1}{2A}\sqrt{\int k(u/h)^2\, du}\sqrt{\int
      k(u/h')^2\, du}}
  =\frac{\frac{1}{2A}\int_{x=-A}^{A} k(x/h)k(x/h')\, dx}{\frac{1}{2A}\sqrt{\int k(u/h)^2\, du}\sqrt{\int k(u/h')^2\, du}}  \\
  & =\frac{\int_{x=-\infty}^\infty k(x/h)k(x/h')\, dx}{\sqrt{\int k(u/h)^2\,
      du}\sqrt{\int k(u/h')^2\, du}}
\end{align*}
for $h\le 1$ (the last step follows since, for $h\le 1$, the integral is over
$-Ah\le x\le Ah$ for both the last and second to last line). Thus,
$\hat{\mathbb{H}}_j(h)$ and $\mathbb{H}(h)$ have the same covariance function
and, for large enough $T$, have approximately the same distribution.

# Looking up and computing snooping-adjusted critical values

```{r}
library("BWSnooping")

## [[TODO]]
```

# Tables and graphs of critical values

The tables and graphs in the paper can be reproduced using the functions
`DFSnoopingCV` and `SnoopingTablesGraphs`. `DFSnoopingCV` computes a data frame
of critical values, and `SnoopingTablesGraphs` reproduces tables and graphs
reported in the paper:

```{r}

## The function DFSnoopingCV may long time to compute, the package has results
## stored for [[TODO]] DFSnoopingCV(S=1000, T=1000, grid.length=500) under the data frame
## snoopingcvs

r <- SnoopingTablesGraphs(snoopingcvs)
```

## Tables for two-sided critical values

- For Nadarya-Watson regression, boundary and interior critical values coincide
- In the tables, "u" stands for uniform, "e" for Epanechnikov, and "t" for
  triangular kernel, so that "0.9u" corresponds to 90\%-level critical value for
  the uniform kernel, "0.99t" corresponds to 99\%-level critical value for
  the triangular kernel, and so on.

```{r, results="asis"}
t1 <- subset(r$table.twosided, boundary==TRUE & order==0)[, -c(1, 2)]
knitr::kable(t1, row.names=FALSE, digits=2,
    caption="Boundary Nadaraya-Watson regression")

t2 <- subset(r$table.twosided, boundary==FALSE & order==0)[, -c(1, 2)]
knitr::kable(t2, row.names=FALSE, digits=2,
    caption="Interior Nadaraya-Watson regression")

t3 <- subset(r$table.twosided, boundary==TRUE & order==1)[, -c(1, 2)]
knitr::kable(t3, row.names=FALSE, digits=2,
    caption="Boundary local linear regression")

t4 <- subset(r$table.twosided, boundary==FALSE & order==1)[, -c(1, 2)]
knitr::kable(t4, row.names=FALSE, digits=2,
    caption="Interior local linear regression")

t5 <- subset(r$table.twosided, boundary==TRUE & order==2)[, -c(1, 2)]
knitr::kable(t5, row.names=FALSE, digits=2,
    caption="Boundary local quadratic regression")

t6 <- subset(r$table.twosided, boundary==FALSE & order==2)[, -c(1, 2)]
knitr::kable(t6, row.names=FALSE, digits=2,
    caption="Interior local quadratic regression")
```


## Tables for one-sided critical values

```{r, results="asis"}
o1 <- subset(r$table.onesided, boundary==TRUE & order==0)[, -c(1, 2)]
knitr::kable(o1, row.names=FALSE, digits=2,
    caption="Boundary Nadaraya-Watson regression")

o2 <- subset(r$table.onesided, boundary==FALSE & order==0)[, -c(1, 2)]
knitr::kable(o2, row.names=FALSE, digits=2,
    caption="Interior Nadaraya-Watson regression")

o3 <- subset(r$table.onesided, boundary==TRUE & order==1)[, -c(1, 2)]
knitr::kable(o3, row.names=FALSE, digits=2,
    caption="Boundary local linear regression")

o4 <- subset(r$table.onesided, boundary==FALSE & order==1)[, -c(1, 2)]
knitr::kable(o4, row.names=FALSE, digits=2,
    caption="Interior local linear regression")

o5 <- subset(r$table.onesided, boundary==TRUE & order==2)[, -c(1, 2)]
knitr::kable(o5, row.names=FALSE, digits=2,
    caption="Boundary local quadratic regression")

o6 <- subset(r$table.onesided, boundary==FALSE & order==2)[, -c(1, 2)]
knitr::kable(o6, row.names=FALSE, digits=2,
    caption="Interior local quadratic regression")
```


## Graphs

Critical values for local constant and local linear regression in the interior:
```{r  message=FALSE, dev="tikz", out.width="0.7\\textwidth"}
r$cv.interior
```

Critical values for local constant and local linear regression at the boundary:
```{r  message=FALSE, dev="tikz", out.width="0.7\\textwidth"}
r$cv.boundary
```

Coverage of unadjusted CIs for local constant and local linear regression in the
interior:
```{r  message=FALSE, dev="tikz", out.width="0.7\\textwidth"}
r$cov.interior
```

Coverage of unadjusted CIs for local constant and local linear regression at the
boundary:
```{r  message=FALSE, dev="tikz", out.width="0.7\\textwidth"}
r$cov.boundary
```



# References
